---
title: "thoblo's website"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
library(plotly)
library(heatmaply)
library(protoclust)
library(spotifyr)
library(compmus)
source('spotify.R')
source('playlists.R')
```

### Gemiddeldes spotify features van koren en Top100

```{r}
Gemiddeldes_top100_lijst <- c(mean(top_100_over_alle_jaren$energy, na.rm = TRUE), mean(top_100_over_alle_jaren$danceability, na.rm = TRUE), mean(top_100_over_alle_jaren$speechiness, na.rm = TRUE), mean(top_100_over_alle_jaren$acousticness, na.rm = TRUE), mean(top_100_over_alle_jaren$liveness, na.rm = TRUE), mean(top_100_over_alle_jaren$valence, na.rm = TRUE))
Gemiddeldes_koren_lijst <- c(mean(Alle_koren_liedjes$energy, na.rm=TRUE), mean(Alle_koren_liedjes$danceability, na.rm=TRUE), mean(Alle_koren_liedjes$speechiness, na.rm=TRUE), mean(Alle_koren_liedjes$acousticness, na.rm=TRUE), mean(Alle_koren_liedjes$liveness, na.rm=TRUE), mean(Alle_koren_liedjes$valence, na.rm=TRUE))
Feature <- c("Energy", "Danceability", "Speechiness", "Acousticness", "Liveness", "Valence")
Value <- Gemiddeldes_top100_lijst
Gemiddeldes_top100 <- tibble(Feature, Value) %>% mutate(Type = "Top100")
Value <- Gemiddeldes_koren_lijst
Gemiddeldes_koren <- tibble(Feature,Value) %>% mutate(Type = "Koren")
Gemiddeldes_top100_en_koren <- Gemiddeldes_top100 %>% bind_rows(Gemiddeldes_koren)

ggplot(Gemiddeldes_top100_en_koren, aes(factor(Feature), Value, fill = Type)) + 
  geom_bar(stat="identity", position = "dodge") + 
  scale_fill_brewer(palette = "Set1") +
  labs(                        
    x = "Feature",
    y = "Waarde"
  ) +
  theme(legend.title=element_blank())
```

### Spotify features door de jaren heen

```{r}
plot(x = jaartallen_lijst, y = Gemiddelde_energy_per_jaar_lijst, type="l", col="blue",ylim = c(0,1), xlab = "Jaartal", ylab = "Waarde")
lines(x = jaartallen_lijst, y = Gemiddelde_danceability_per_jaar_lijst, type="l", col="pink")
lines(x = jaartallen_lijst, y = Gemiddelde_speechiness_per_jaar_lijst, type="l", col="green")
lines(x = jaartallen_lijst, y = Gemiddelde_acousticness_per_jaar_lijst, type="l", col="red")
lines(x = jaartallen_lijst, y = Gemiddelde_liveness_per_jaar_lijst, type="l", col="purple")
lines(x = jaartallen_lijst, y = Gemiddelde_valence_per_jaar_lijst, type="l", col="black")
legend(1965, 1.02, legend=c("Energy", "Danceability","Speechiness", "Acousticness", "Liveness", "Valence"),
       col=c("blue", "pink", "green", "red", "purple", "black"), lty=1, cex=0.5)
```

### Boxplots spotify features voor elk koor

```{r}
#Gemiddelde energy, valence etc van Top 100 alle jaren
Top100EnergyAlleJarenGemiddeld <- mean(top_100_over_alle_jaren$energy, na.rm = TRUE)
Top100DanceabilityAlleJarenGemiddeld <- mean(top_100_over_alle_jaren$danceability, na.rm = TRUE)
Top100SpeechinessAlleJarenGemiddeld <- mean(top_100_over_alle_jaren$speechiness, na.rm = TRUE)
Top100AcousticnessAlleJarenGemiddeld <- mean(top_100_over_alle_jaren$acousticness, na.rm = TRUE)
Top100LivenessAlleJarenGemiddeld <- mean(top_100_over_alle_jaren$liveness, na.rm = TRUE)
Top100ValenceAlleJarenGemiddeld <- mean(top_100_over_alle_jaren$valence, na.rm = TRUE)

#Boxplots van energy, valence etc van alle koren
Alle_koren_energy_plot <-
  Alle_koren %>%
  ggplot(aes(x = Koor, y = energy)) +
  geom_boxplot() +
  xlab("Koren") +
  ylab("Energy") +
  geom_hline(yintercept=Top100EnergyAlleJarenGemiddeld, linetype="dashed")

Alle_koren_danceability_plot <-
  Alle_koren %>%
  ggplot(aes(x = Koor, y = danceability)) +
  geom_boxplot() +
  xlab("Koren") +
  ylab("Danceability") +
  geom_hline(yintercept=Top100DanceabilityAlleJarenGemiddeld, linetype="dashed")

Alle_koren_speechiness_plot <-
  Alle_koren %>%
  ggplot(aes(x = Koor, y = speechiness)) +
  geom_boxplot() +
  xlab("Koren") +
  ylab("Speechiness") +
  geom_hline(yintercept=Top100SpeechinessAlleJarenGemiddeld, linetype="dashed")

Alle_koren_acousticness_plot <-
  Alle_koren %>%
  ggplot(aes(x = Koor, y = acousticness)) +
  geom_boxplot() +
  xlab("Koren") +
  ylab("Acousticness") +
  geom_hline(yintercept=Top100AcousticnessAlleJarenGemiddeld, linetype="dashed")

Alle_koren_liveness_plot <-
  Alle_koren %>%
  ggplot(aes(x = Koor, y = liveness)) +
  geom_boxplot() +
  xlab("Koren") +
  ylab("Liveness") +
  geom_hline(yintercept=Top100LivenessAlleJarenGemiddeld, linetype="dashed")

Alle_koren_valence_plot <-
  Alle_koren %>%
  ggplot(aes(x = Koor, y = valence)) +
  geom_boxplot() +
  xlab("Koren") +
  ylab("Valence") +
  geom_hline(yintercept=Top100ValenceAlleJarenGemiddeld, linetype="dashed")


#Weergeven van plots
Alle_koren_energy_plot
Alle_koren_danceability_plot
Alle_koren_speechiness_plot
Alle_koren_acousticness_plot
Alle_koren_liveness_plot
Alle_koren_valence_plot
```

______
Koor 1 = Firma Vocaal

Koor 2 = Popolo

Koor 3 = Studentenkoort Tilburg

Koor 4 = Vocal Essen

Koor 5 = Plica

Koor 6 = UCK Utrecht


### Energy-Valence scatterplot

```{r}
ScatterEnergyValence <-
  Alle_koren_met_koornaam %>%
  ggplot(                      # Set up the plot.
    aes(
      x = valence,
      y = energy,
      size = loudness,
      colour = Koor,
      label = track.name   # Labels will be interactively visible.
    )
  ) +
  geom_point() +               # Scatter plot.
  geom_rug(size = 0.1) +       # Add 'fringes' to show data distribution.
  scale_x_continuous(          # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),  # Use grid-lines for quadrants only.
    minor_breaks = NULL      # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(          # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(         # Use the Color Brewer to choose a palette.
    type = "qual",           # Qualitative set.
    palette = "Set2",
    guide = "none"          # Name of the palette is 'Set2'.
  ) +
  scale_size_continuous(       # Fine-tune the sizes of each point.
    trans = "exp",           # Use an exp transformation to emphasise loud.
    guide = "none"           # Remove the legend for size.
  ) +
  theme_light() +              # Use a simpler them.
  labs(                        # Make the titles nice.
    x = "Valence",
    y = "Energy",
    colour = "Koor"
  )

ggplotly(ScatterEnergyValence)
```

### Danceability-Acousticness scatterplot
```{r}
ScatterDanceabilityAcousticness <-
  Alle_koren_met_koornaam %>%
  ggplot(                      # Set up the plot.
    aes(
      x = acousticness,
      y = danceability,
      size = loudness,
      colour = Koor,
      label = track.name   # Labels will be interactively visible.
    )
  ) +
  geom_point() +               # Scatter plot.
  geom_rug(size = 0.1) +       # Add 'fringes' to show data distribution.
  scale_x_continuous(          # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),  # Use grid-lines for quadrants only.
    minor_breaks = NULL      # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(          # Fine-tune the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(         # Use the Color Brewer to choose a palette.
    type = "qual",           # Qualitative set.
    palette = "Set2",       # Name of the palette is 'Set2'.
    guide = 'none'
  ) +
  scale_size_continuous(       # Fine-tune the sizes of each point.
    trans = "exp",           # Use an exp transformation to emphasise loud.
    guide = "none"           # Remove the legend for size.
  ) +
  theme_light() +              # Use a simpler them.
  labs(                        # Make the titles nice.
    x = "Acousticness",
    y = "Danceability"
  )
ggplotly(ScatterDanceabilityAcousticness)
```

### Speechiness-Liveness scatterplot

```{r}
ScatterSpeechinessLiveness <-
  Alle_koren_met_koornaam %>%
  ggplot(                      # Set up the plot.
    aes(
      x = liveness,
      y = speechiness,
      size = loudness,
      colour = Koor,
      label = track.name   # Labels will be interactively visible.
    )
  ) +
  geom_point() +               # Scatter plot.
  geom_rug(size = 0.1) +       # Add 'fringes' to show data distribution.
  scale_x_continuous(          # Fine-tune the x axis.
    limits = c(0, 0.50),
    breaks = c(0, 0.50),  # Use grid-lines for quadrants only.
    minor_breaks = NULL      # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(          # Fine-tune the y axis in the same way.
    limits = c(0, 0.50),
    breaks = c(0, 0.50),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(         # Use the Color Brewer to choose a palette.
    type = "qual",           # Qualitative set.
    palette = "Set2",       # Name of the palette is 'Set2'.
    guide = 'none'
  ) +
  scale_size_continuous(       # Fine-tune the sizes of each point.
    trans = "exp",           # Use an exp transformation to emphasise loud.
    guide = "none"           # Remove the legend for size.
  ) +
  theme(legend.position='none') +
  theme_light() +              # Use a simpler them.
  labs(                        # Make the titles nice.
    x = "Liveness",
    y = "Speechiness",
    colour = "Koor"
  )

ggplotly(ScatterSpeechinessLiveness)
```

### Dendrogram en Heatmap

```{r}
Popolo_Heat <- get_playlist_audio_features('02F2tqTr7CSqHTrMwQRANP', '02F2tqTr7CSqHTrMwQRANP') %>%
  add_audio_analysis %>%
  mutate(
    segments = 
      map2(segments, key, compmus_c_transpose)) %>% 
  mutate(
    pitches = 
      map(segments, 
          compmus_summarise, pitches, 
          method = 'mean', norm = 'manhattan'),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = 'mean')) %>% 
  mutate(pitches = map(pitches, compmus_normalise, 'clr')) %>% 
  mutate_at(vars(pitches, timbre), map, bind_rows) %>% 
  unnest(cols = c(pitches, timbre))
  
  
Popolo_Heat_juice <- 
  recipe(track.name ~
           danceability +
           energy +
           loudness +
           speechiness +
           acousticness +
           instrumentalness +
           liveness +
           valence +
           tempo +
           duration +
           C + `C#|Db` + D + `D#|Eb` +
           E + `F` + `F#|Gb` + G +
           `G#|Ab` + A + `A#|Bb` + B +
           c01 + c02 + c03 + c04 + c05 + c06 +
           c07 + c08 + c09 + c10 + c11 + c12,
         data = Popolo_Heat) %>% 
  step_range(all_predictors()) %>% 
  prep(Popolo_Heat %>% mutate(track.name = str_trunc(track.name, 20))) %>% 
  juice %>% 
  column_to_rownames('track.name')


Alle_koren_liedjess <- get_playlist_audio_features('5uA0ByhoDZ2WouF0Oq6Ab4', '5uA0ByhoDZ2WouF0Oq6Ab4') %>%
  add_audio_analysis %>%
  mutate(
    segments = 
      map2(segments, key, compmus_c_transpose)) %>% 
  mutate(
    pitches = 
      map(segments, 
          compmus_summarise, pitches, 
          method = 'mean', norm = 'manhattan'),
    timbre =
      map(
        segments,
        compmus_summarise, timbre,
        method = 'mean')) %>% 
  mutate(pitches = map(pitches, compmus_normalise, 'clr')) %>% 
  mutate_at(vars(pitches, timbre), map, bind_rows) %>% 
  unnest(cols = c(pitches, timbre))
  
  
Alle_koren_juice <- 
  recipe(track.name ~
           danceability +
           energy +
           loudness +
           speechiness +
           acousticness +
           instrumentalness +
           liveness +
           valence +
           tempo +
           duration +
           C + `C#|Db` + D + `D#|Eb` +
           E + `F` + `F#|Gb` + G +
           `G#|Ab` + A + `A#|Bb` + B +
           c01 + c02 + c03 + c04 + c05 + c06 +
           c07 + c08 + c09 + c10 + c11 + c12,
         data = Alle_koren_liedjess) %>% 
  step_range(all_predictors()) %>% 
  prep(Alle_koren_liedjess %>% mutate(track.name = str_trunc(track.name, 20))) %>% 
  juice %>% 
  column_to_rownames('track.name')

ggheatmap(
  Popolo_Heat_juice,
  hclustfun = protoclust,
  dist_method = 'manhattan'
)
ggheatmap(
  Alle_koren_juice,
  hclustfun = protoclust,
  dist_method = 'manhattan'
)
```

### Chroma en Timbre features

```{r}
WithinTemptation <- 
  get_tidy_audio_analysis('66wcihY2Y8ZSqux6EivMWa') %>% 
  compmus_align(bars, segments) %>% 
  select(bars) %>% unnest(bars) %>% 
  mutate(
    pitches = 
      map(segments, 
          compmus_summarise, pitches, 
          method = 'acentre', norm = 'manhattan')) %>% 
  mutate(
    timbre = 
      map(segments, 
          compmus_summarise, timbre, 
          method = 'mean'))
WithinTemptationplot <- 
  bind_rows(
    WithinTemptation %>% compmus_self_similarity(pitches, 'aitchison') %>% mutate(d = d / max(d), type = "Chroma - Within Temptation"),
    WithinTemptation %>% compmus_self_similarity(timbre, 'euclidean') %>% mutate(d = d / max(d), type = "Timbre - Within Temptation")) %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2, 
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d)) + 
  geom_tile() +
  coord_fixed() +
  facet_wrap(~ type) +
  scale_fill_viridis_c(option = 'E', guide = 'none') +
  theme_classic() +
  labs(x = '', y = '')

Evanescence <- 
  get_tidy_audio_analysis('0COqiPhxzoWICwFCS4eZcp') %>% 
  compmus_align(bars, segments) %>% 
  select(bars) %>% unnest(bars) %>% 
  mutate(
    pitches = 
      map(segments, 
          compmus_summarise, pitches, 
          method = 'acentre', norm = 'manhattan')) %>% 
  mutate(
    timbre = 
      map(segments, 
          compmus_summarise, timbre, 
          method = 'mean'))
Evanescenceplot <- 
  bind_rows(
    Evanescence %>% compmus_self_similarity(pitches, 'aitchison') %>% mutate(d = d / max(d), type = "Chroma - Evanescence"),
    Evanescence %>% compmus_self_similarity(timbre, 'euclidean') %>% mutate(d = d / max(d), type = "Timbre - Evanescence")) %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2, 
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d)) + 
  geom_tile() +
  coord_fixed() +
  facet_wrap(~ type) +
  scale_fill_viridis_c(option = 'E', guide = 'none') +
  theme_classic() +
  labs(x = '', y = '')


subplot(WithinTemptationplot,Evanescenceplot, nrows = 2)
```
